---
title: "A Few of My Favorite Things"
author: "[*Adam Sisco*](https://awsisco.github.io)"
date: "June 28, 2019"
output: html_document
---

# {.tabset .tabset-fade}
Here you'll find some running lists with a few of my favorite things on the Web. No raindrops or whiskers here but plenty of other cool stuff.

## Graphics & Data Viz
Some data visualizations I think are important, novel, or inspiring.

```{r, echo=FALSE}
library(magrittr)
library(knitr)
library(kableExtra)
library(jsonlite)
library(tools)

viz_df <- fromJSON("lists/data_viz.json")
colnames(viz_df) <- toTitleCase(colnames(viz_df))

viz_df %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, width = "35%") %>%
  column_spec(2, width = "20%") %>%
  column_spec(3, width = "45%")
```

## Cheat Sheets
A collection of cheat sheets and reference resources with a proven record of making my life easier.

__Color__

* [NCL Named Colors](https://www.ncl.ucar.edu/Document/Graphics/named_colors.shtml){target="_blank"}
* [NCL Color Table Gallery](https://www.ncl.ucar.edu/Document/Graphics/color_table_gallery.shtml){target="_blank"}
* [ColorBrewer](http://colorbrewer2.org){target="_blank"}

__R & RStudio__

* [RStudio Cheat Sheets](https://www.rstudio.com/resources/cheatsheets/){target="_blank"}

__Web Development__

* [CSS Flexbox Cheat Sheet](https://yoksel.github.io/flex-cheatsheet/){target="_blank"}
* [HTML Color Names](https://www.w3schools.com/colors/colors_names.asp){target="_blank"}

## *xkcd* Comics
Some of my favorite *xkcd* comics.

* [University Website](https://xkcd.com/773/){target="_blank"}
* [Standards](https://xkcd.com/927/){target="_blank"}

## Reproducible Research

```{r, echo=FALSE}
rr_df <- fromJSON("lists/reproducible_research.json")
colnames(rr_df) <- toTitleCase(colnames(rr_df))

rr_df %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```
